Sensitivity Analysis

### 2022-09-20 analysis/06_sensitivity_analysis.Rmd
Add sensitivity analysis stuff

1. Min time series duration
```{r}
dur_dfs <- list(min3 = filter(model_data, duration > 2),
                min4 = filter(model_data, duration > 3),
                min5 = filter(model_data, duration > 4))

duration_sens <- map_dfr(dur_dfs, ~pmap_dfr(mods, get_model, data = .x), .id = "dataID")
```

2. Inclusion of Amphibians - nothing changes when you exclude them 
```{r}
no_amph <- pmap_dfr(mods, get_model, data = model_data %>% filter(taxa != "Amphibians")) %>%
  mutate(dataID = no_amph)

# this annoyingly doesn't work because of some dataframe column
# sens_models <- bind_rows(bind_cols(select(duration_sens, -dataID), pull(duration_sens, dataID)) %>% select(-model, -formula), 
#                          no_amph %>% select(-model, -formula))

save(duration_sens, no_amph, file = here::here("data/sensitivity_models.rda"))
```

@@

covg_dfs <- list(covg75 = filter(model_data),
                covg85 = filter(model_data, coverage >= 0.85),
                covg90 = filter(model_data, coverage >= 0.90))

coverage_sens <- map_dfr(covg_dfs, ~pmap_dfr(mods %>% 
                                               filter(metric_name %in% c("FRic", "FDiv", "FEve", "S", "SES_FRic",
                                                                         "SES_FDiv", "SES_FEve"), 
                                                      model_id == "base"), 
                                             get_model, data = .x), .id = "dataID")

```

>>>>

1. Min time series duration
```{r}
dur_dfs <- list(min3 = filter(model_data, taxa != "Amphibians", duration > 2),
                min4 = filter(model_data, taxa != "Amphibians", duration > 3),
                min5 = filter(model_data, taxa != "Amphibians", duration > 4))

duration_sens <- map_dfr(dur_dfs, ~pmap_dfr(filter(mods, model_id == "base"), get_model, data = .x), .id = "dataID")
```

2. Inclusion of Amphibians - nothing changes when you exclude them 
```{r}
with_amph <- pmap_dfr(filter(mods, model_id == "base"), get_model, data = model_data) %>%
  mutate(dataID = "with_amph")
```

@@

covg_dfs <- list(covg75 = filter(model_data, taxa != "Amphibians"),
                covg85 = filter(model_data, taxa != "Amphibians", coverage >= 0.85),
                covg90 = filter(model_data, taxa != "Amphibians", coverage >= 0.90))

coverage_sens <- map_dfr(covg_dfs, ~pmap_dfr(filter(mods, model_id == "base"), 
                                             get_model, data = .x), .id = "dataID")

sens_mods <- bind_rows(duration_sens, coverage_sens, with_amph) %>%
  select(-model) %>%
  filter(metric != "Jaccard_next") %>%
  write_csv(here::here("paper", "sensitivity_models.csv"))
```
